Title

### 2020-02-05 manuscript.Rmd
added some print strings

Anywhere from 18 to 30 samples is reasonable.
At 3 cores 5 taxa:
Minimum 4 samples per core 
Maximum 9 samples per core
```{r}
signif(M/3, 3)
```
At 2 cores 5 taxa:
Minimum 7 samples per core
Maximum 14 samples per core
```{r}
signif(M/2, 3)
```

>>>>

Anywhere from 18 to 30 samples is reasonable.
At 3 cores 5 taxa:
Minimum 4 samples per core 
Maximum 9 samples per core
```{r}
print('No. of samples at Three Cores')
signif(M/3, 3)
```
At 2 cores 5 taxa:
Minimum 7 samples per core
Maximum 14 samples per core
```{r}
print('No. of samples at Two Cores')
signif(M/2, 3)
```
